\textbf{Computational Fuzzy Extractors}

### 2013-03-01 CompFuzzExt.tex
Added discussion of LWE based PRG removed conductor language

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\textbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}

@@

\begin{definition}%\protect{\cite[Definition 5]{DBLP:journals/siamcomp/DodisORS08}}
An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' (\gen) and ``reproduce'' (\rep), with the following properties:
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability at least $1-\delta$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

Secure sketches are the main technical tool in the construction of fuzzy extractors.  They produces a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}%\protect{\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:secure sketch}
An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' (\sketch) and ``recover'' (\rec), with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

@@

\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext$ be an average-case $(n, \tilde{m}, \ell, \epsilon)$-strong extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ set $P=(\sketch(w), x), R=\ext(w;x)$, and output $(R,P)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $R=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction, specifically, the entropy loss in the definition of the secure sketch~($m-\tilde{m}$).  %The cause for the entropy loss in the secure sketch is the additional bits added for error correction.  In the definition of a fuzzy extractor this is the input min-entropy less the size of the output: $m-\ell$.   
%The entropy loss in the fuzzy extractor is due to the use of an extractor (where the loss is inversely proportional to the statistical distance of the output distribution from uniform) and the use of the secure sketch.

%=============================================================
\section{Defining Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
We first recall a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}, as extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.

@@

\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.  A reasonable question to ask is whether a sketch could retain unpredictability of the source.  We begin by defining conditional unpredictability entropy:

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
For a distribution $(X, Z)$, we say that $X$ has unpredictability entropy at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\forall D\in \mathcal{D}_{s_{sec}}, \delta^D((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
\Pr[C(Z) = Y ] \leq 2^{-k}
.\]
\end{definition}
We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{lem:unp extraction} 
Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
\end{lemma}
Thus, using a sketch that retained unpredictability entropy and a reconstructive extractor we could build a computational fuzzy extractor~(in a similar fashion to \lemref{lem:fuzzy ext construction}).  Unfortunately, we show that the unpredictability entropy must decrease with the $O(\log B_t(\cdot))$.  
\begin{theorem}
Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} = \Omega(|\rec|+b)$, then $\tilde{m}\leq b - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
\end{theorem}
Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} = \Omega(|\rec|+b)$.  Let $Y_{W=w \wedge \sketch(w) = s} $ be a collection of distributions giving rise to a joint distribution $Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))\leq \epsilon$.  It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(\sketch(W)) = Y]\geq 2^{\tilde{m}}$ where $\tilde{m} = n - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.  We begin by showing that $Y$ must correctly recover most of the time.
\begin{claim}
\label{clm:y is recoverable}
\Pr[\rec(B_t(Y), \sketch(W)) = Y]&=\\
\Pr[y\leftarrow Y\wedge y'\leftarrow B_t(y) \wedge \rec(y', s) = y] &=\\ 
\Pr[w\leftarrow W, s\leftarrow \sketch(w), \wedge y \leftarrow Y_{s} \wedge y' \leftarrow B_t(y) \wedge \rec(y', s) =y ] &\geq 1-\epsilon -\delta.
Suppose that $\Pr[\rec(B_t(Y), \sketch(W)) = Y]<1-\epsilon -\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
\item Input $x\in \zo^b, s\in\zo^*$.
\item Sample $x'\leftarrow B_t(x)$.
\item Output $1$ if $\rec(x', s) = x$ otherwise output $0$.
Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in\zo^b$ such that \[\dis(w, w')\leq t, \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This immediately implies that $\Pr[\rec(W, \sketch(W))  ]\geq 1-\delta$.  The statement of the claim follows as 
\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(Y, \sketch(W))] &=\\
\Pr[\rec(B_t(W), \sketch(W) )= W] - \Pr[\rec(B_t(Y), \sketch(W)) = Y] &> (1-\delta)-(1-\delta - \epsilon)>\epsilon.
We now consider a fixed $w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_{s}, y'\leftarrow B_t(y)$ and define the quantity $P_{y' , s, y} = \Pr[\rec(y', s) =y]$.  \clref{clm:y is recoverable} says that 
 \Pr[w\leftarrow W, s\leftarrow \sketch(w), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) =y' | Y = y] P_{y',  s, y} \geq 1-\delta -\epsilon.
We note that for any particular $y, y'$ such that $\dis(y, y')\leq t, \Pr[B_t(y) = y' | Y=y] = 1/|B_t(\cdot)|$ and if $\dis(y, y')>t, Pr[B_t(y) = y' | Y=y] = 0$.  We restate this as $y, y', \Pr[B_t(y) = y' | Y=y] \leq 1/|B_t(\cdot)|$
We now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
\item Input $s\in\zo^*$.
\item Sample $x'\leftarrow \zo^b$.
\item Output $\rec(x', s)$.
We define by $X$ the random variable corresponding to the sample $x'$ performed by $\mathcal{I}_t$.
We now show that $\mathcal{I}$ predicts $Y$, defining :
2^{\tilde{m}}& = \Pr[\mathcal{I}(\sketch(W)) = Y] \\
&= \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \Pr[\mathcal{I}(s) = y]\\
&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ]\Pr[\mathcal{I}(s) = y | X = y']\\
&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[X = y' ] P_{y', s, y}\\
&\geq \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{\Pr[X = y']}{\Pr[B_t(y) = y' | Y = y]}\Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
&\geq  \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \frac{|B_t(\cdot)|}{2^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
&\geq \frac{|B_t(\cdot)|}{2^b} \Pr[w\leftarrow W, s\leftarrow \sketch(W), y\leftarrow Y_s] \sum_{y'\in \zo^b} \Pr[B_t(y) = y' | Y=y ] P_{y', s, y}\\
&\geq \frac{|B_t(\cdot)|}{2^b}(1-\epsilon - \delta)
Finally converting to entropy, one has $\tilde{m}\leq b-\log |B_t(\cdot)| - \log (1-\epsilon - \delta)$.
This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The two statements are incomparable.
\subsection{Defining  Computational Fuzzy Conductors}
\label{sec:unp secure sketch}
In \secref{sec:imp HILL sketch}, we showed that defining a  computational fuzzy conductor using HILL entropy connects the parameters to the best information-theoretic sketches.  The basic problem is that an adversary had access to both $X$ and $SS(X)$ and could test if neighborhoods correctly decoded.  However, our sketch outputs a new random variable, this problem does not occur.  Instead of building a computational sketch, we will build a computational conductor.  We adapt the definition of a fuzzy conductor from~\cite{KanukurthiR09} to the computational setting:
%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
%\end{definition}
%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.  We begin by defining unpredictability entropy:

>>>>

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\textbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}

@@

\begin{definition}%\protect{\cite[Definition 5]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:fuzzy extractor}
An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability at least $1-\delta$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

Secure sketches are the main technical tool in the construction of fuzzy extractors.  They produces a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}%\protect{\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:secure sketch}
An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

@@

\begin{lemma}%\protect{\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext$ be an average-case $(n, \tilde{m}, \ell, \epsilon)$-strong extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ set $P=(\sketch(w), x), R=\ext(w;x)$, and output $(R,P)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $R=\ext(w;x)$.
\end{itemize}
\end{lemma}
The main parameter we will be concerned with is the entropy loss of the construction.  We relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.

\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, m, \ell, t)$-\emph{computational fuzzy extractor} is that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  %%Furthermore \rep is computable by a circuit of size at most $s_{rec}$.  
If $d(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ has full HILL entropy conditioned on $P$, that is $H^\hill_{\epsilon, s_{sec}}(R | P) = \ell$.
\end{itemize}
\end{definition}
Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.% ($s_{rec}$ is the size of the circuit that computes \rec and $s_{sec}$ is unbounded).

It seems natural to construct a computational fuzzy extractor using a sketch that retains computational entropy and then a randomness extractor.  In the next section, we show this paradigm is difficult to realize.

%\textbf{Note: }A computational fuzzy extractor could also be constructed by making the extractor computational~(using a standard extractor and then running a pseudorandom generator on its output).  We compare the two approaches in \secref{sec:prg based comparison} after presenting our construction.
%, specifically, the entropy loss in the definition of the secure sketch~($m-\tilde{m}$).  %The cause for the entropy loss in the secure sketch is the additional bits added for error correction.  In the definition of a fuzzy extractor this is the input min-entropy less the size of the output: $m-\ell$.   
%The entropy loss in the fuzzy extractor is due to the use of an extractor (where the loss is inversely proportional to the statistical distance of the output distribution from uniform) and the use of the secure sketch.

%=============================================================
\section{Impossibility of Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational entropy than information theoretic entropy.  %We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the unpredictability of a sketch must decrease with the number of neighbors of a point in the metric space.  These results are strongest for high entropy sources.  The results get weaker as we consider sources with lower starting entropy.  If a source contains points from a good error code, then the sketch procedure does not need to output any public value so no drop occurs in entropy.

\subsection{Bounds on Secure Sketches using HILL entropy}
\label{sec:imp HILL sketch}
We recall a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}, as extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.

@@

\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
\label{sec:imp unp sketch}
In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.  A reasonable question to ask is whether a sketch could retain unpredictability of the source.  We begin by defining conditional unpredictability entropy:

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
For a distribution $(X, Z)$, we say that $X$ has \emph{unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
\[
\Pr[C(Z) = Y ] \leq 2^{-k}
.\]
\end{definition}
We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy}$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfied \defref{def:secure sketch} with the security requirement replaces with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{lem:unp extraction} 
Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
\end{lemma}
Thus, using a sketch that retained unpredictability entropy and a reconstructive extractor we could build a computational fuzzy extractor~(in a similar fashion to \lemref{lem:fuzzy ext construction}).

Unfortunately, unpredictability entropy must also depend on $t$.  An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.  %That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.  
The formal statement is below:
\begin{theorem}
\label{thm:imp of unp entropy}
Let $W$ be a distribution over $\zo^b$ and let $(\sketch, \rec)$ be an Unpredictability-entropy $(\zo^b, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} = \Omega(|\rec|+b)$, then $\tilde{m}\leq b - \log |B_t(\cdot)| + \log(1-\epsilon -\delta)$.
\end{theorem}
This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.  This means we cannot construct a good code out of the points of $Y$.  In \secref{sec:proof of imp unp entropy}, we prove a stronger version of \thref{thm:imp of unp entropy}, based on a relaxed notion of unpredictability entropy.%Our bound is a result of the Hamming bound for the space.

\textbf{Avoiding lower bounds from \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy}:}

The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.  The results get weaker as we consider sources with lower starter entropy.  This is necessary, if a source contains only codewords (of an error correcting code), no sketch is necessary.  This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.

Both of the lower bound results arise because the reduction can ensure that \rec functions as an error-correcting code for many points of the output distribution.  It may be possible to avoid this problem if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.  This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).}.  An algorithm that outputs a fresh random variable would be a computational fuzzy conductor~(see~\cite{KanukurthiR09} for the definition of a fuzzy conductor).  Our construction~(in \secref{sec:fuzzyCompExt}) has pseudorandom output and immediately satisfies definition of a computational fuzzy extractor~(\defref{def:comp fuzzy extractor}).  It is unknown if a more efficient construction could be achieved using a computational fuzzy conductor that is not also a computational fuzzy extractor.
\bnote{Not happy with this wording, revise}

%\subsection{Defining  Computational Fuzzy Conductors}
%\label{sec:unp secure sketch}
%In Sections \ref{sec:imp HILL sketch} and \ref{sec:imp unp sketch}, we showed lower bounds on an entropy drop of computational sketches.  If, the error correcting algorithm outputs a new random variable, bounds do not apply.  Instead of building a computational sketch, we will build a computational conductor.  We adapt the definition of a fuzzy conductor from~\cite{KanukurthiR09} to the computational setting:
%%\begin{definition}\protect{\cite[Definition]{KanukurthiR09}}
%%The procedures $(\sketch, \rec)$ are an $(\mathcal{M}, m, \tilde{m},t, \epsilon)$-\emph{weakly robust fuzzy conductor} if:
%%\begin{enumerate}
%%\item Error Tolerance: If $\dis(w, w')\leq t$ and $s\leftarrow \sketch(w)$, then $\Pr[\rec(w', \sketch(w)) \neq  \rec(w, \sketch(w))] \leq \epsilon$ where the probability is over the coins of $\sketch, \rec$.
%%\item Security of $\sketch$: If $H_\infty(W) \geq m$, then $\Hav(\rec(W, \sketch(W)) | \sketch(W))\geq \tilde{m}$.
%%\end{enumerate}
%%\end{definition}
%%We will essentially build %if we define the secure sketch using unpredictability entropy~\cite[Section 5]{DBLP:conf/eurocrypt/HsiaoLR07}, this oracle is not available to the adversary.  We begin by defining unpredictability entropy:
%
%
%%We now provide a definition of a robust computational sketch using unpredictability entropy:
%\begin{definition}\label{def:comp secure sketch}
%A pair of randomized procedures $(\sketch, \rec)$ is a $(\mathcal{M},m, \tilde{m}, \epsilon,  t)$-\emph{computational fuzzy conductor} if the following properties hold:
%\begin{enumerate}
%\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$ and runs in expected time $s_{sketch}$.
%\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $d(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))\neq \rec(w, \sketch(w))] = \delta$ and \rec runs in expected time $s_{rec}$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.  
%\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the output $\rec$ has high HILL entropy given $\sketch(W)$.  That is, $H^{\hill}_{\epsilon, s_{sec}}(\rec(W, \sketch(W))|\sketch(W))\geq \tilde{m}$.
%\end{enumerate}
%We say that $(\sketch, \rec)$ is $(\epsilon, s_{sec})$-secure with error probability $\delta$.
%If $m=\tilde{m}$ we say a conductor is \emph{lossless} and we omit the parameter $\tilde{m}$.
%\end{definition}
%
%%We make $s_{sketch}, s_{rec}$ explicit in the definition as we are considering computationally bounded adversaries and the definition is only meaningful if both $s_{rec}$ and $s_{sketch}$ are significantly smaller than $s_{sec}$.  
%In \secref{sec:comp fuzzy extractors}, we show a natural construction of a computational fuzzy extractor from a computational fuzzy conductor that meets \defref{def:comp secure sketch}.  We show in the next section that a lossless construction is achievable for the uniform distribution using the $\LWE$ problem.

\section{Computational Fuzzy Extractor based on \class{LWE}}
\label{sec:fuzzyCompExt}

In this section we describe our main construction.  Our construction uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} instantiated with a random linear code over a finite field $\Fq$.   Let $\mathcal{I}_t$ be an algorithm that decodes a random linear code with at most $t$ errors~(not necessarily efficient).  We provide an informal description below.
%Please refer to \consref{cons:informal construction} for the description of the construction.

\begin{construction}
Let $n$ be a security parameter and let $m>n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\mathcal{I}_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Compute $p = (\vA, \vA X+w)$, \\\ $r = X_{1,...,n/2}$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
\item Let $X = \mathcal{I}_t(\vA, \vect{D})$\\
\item Output $X_{1,...,n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|P) \approx \Hoo(W)$.  Efficiency comes from the fact that up to some number of errors $t$, decoding is easy and thus $\mathcal{I}_t$ can be made polynomial-time.

The rest of this section is devoted to making these intuitive statements precise.
 We describe the \class{LWE} problem and the security of our construction in \secref{subsec:LWE}.
 %a recent variant due to D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} in \secref{subsec:LWE}.  
We describe conditions for efficient decoding in \secref{sec:time main construction}.  In \secref{sec:lossless extractor} we describe parameter settings where our construction yields a lossless secure sketch.  In \secref{sec:prg based comparison} we compare \consref{cons:informal construction} to using a information-theoretic fuzzy extractor and running a pseudorandom generator on the output.\lnote{revise after going through the rest}.
